\documentclass[a4paper,10pt]{article}
%\documentclass[a4paper,10pt]{scrartcl}

\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\usepackage[top=2.5cm]{geometry}

\title{}
\author{}
\date{}

\pdfinfo{%
  /Title    ()
  /Author   ()
  /Creator  ()
  /Producer ()
  /Subject  ()
  /Keywords ()
}

\begin{document}

\section{lambdakzeroBuilder}
(??? what if not useAbsDCA? is this really all in [cm]?)
\begin{itemize}
 \item V0
 \begin{itemize}
 \item min. radius (0.9 cm)
 \item min. $\cos(\theta)$ (0.995)
 \item max. DCA between daughters (1.0 cm)
 \end{itemize}
 \item V0 daughters
 \begin{itemize}
 \item min. DCAxy to PV (0.1 cm)
 \item min. TPC crossed rows (70)
 \end{itemize}

\end{itemize}


\section{HfTrackIndexSkimCreatorTagSelTracks}
(cuts on bachelor track)
\begin{itemize}
\item quality checks (true)
\begin{itemize}
\item useIsGlobalTrack (false)
\item useIsGlobalTrackWoDCA (false)
\item min. TPC found clusters (70)
\end{itemize}
 \item min. $p_T$ (0.3 GeV)
 \item max $|\eta|$ (0.8)
 \item DCAxy ($p_T$ $<$ 2 GeV: 0.0025cm $<$ DCAxy $<$ 10cm,\\ \hspace*{1.4cm}$p_T$ $>$ 2 GeV: 0cm $<$ DCAxy $<$ 10cm)
\end{itemize}

\section{HfTrackIndexSkimCreatorCascades}

\begin{itemize}
 \item candidate
 \begin{itemize}
 \item max. $|m-m(\Lambda_c)|$ (1.0 GeV)
 \item min. $p_T$ (0 GeV)
 \textcolor{gray}{\item max. R (200 cm(?))}
  \end{itemize}
 \item bachelor
 \begin{itemize}
 \item TPCrefit (true)
 \item min. TPC crossed rows (50)
 \end{itemize}
 \item V0
 \begin{itemize}
 \item max. $|m - m(K_S^0)|$ (50 MeV)
 \item min. $\cos(\theta)$ (0.995)
 \end{itemize}
 \item V0 daughters
  \begin{itemize}
 \item TPCrefit (true)
 \item min. TPC min. crossed rows (50)
 \item max. $|\eta|$ (1.1)
 \item min. $p_T$ (0.05 GeV)
 \end{itemize}
\end{itemize}
\textcolor{gray}{
\section{HfTrackIndexSkimCreatorCascades}
(TODO: set magentic field from CCDB !!!)
\begin{itemize}
  \item max. R (200 cm(?))
  \item max. dZ (4 cm(?))
\end{itemize}
}
\section{HfCandidateSelectorLcToK0sP}
\begin{itemize}
 \item candidate
 \begin{itemize}
 \item $p_T$ ($1\,\rm{GeV} < p_T < 24\,\rm{GeV}$)
 \end{itemize}
 \item bachelor
 \begin{itemize}
 \item min. $p_T$ (0.5 GeV - 1.0 GeV)
 \item max. DCAxy (0.05 cm - 0.2 cm)
 \item PID (true):
 \begin{itemize}
 \item max. $|n\sigma^{\rm{TPC}}|$ ($p < 1$ GeV: 2, $p>1$ GeV: $\infty$)
 \item max. $|n\sigma^{\rm{TOF}}|$ ($p < 1$ GeV: $\infty$, $p>1$ GeV: 3)
 \end{itemize}
 \end{itemize}
 \item V0
 \begin{itemize}
 \item min. $p_T$ (0.6 GeV - 1.9 GeV)
 \item max. DCAxy ($\infty$)
 \item max. $|m - m(K_S^0)|$ (8 MeV - 19 MeV)
 \item min. $|m - m(\Lambda)|$ (5 MeV)
 \item min. $|m - m(\gamma)|$ (100 MeV)
 \end{itemize}
 \item V0 daughters
 \begin{itemize}
 \item min. $p_T$ (0.3 GeV - 0.4 GeV)
 \end{itemize}
\end{itemize}


\end{document}
